---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, message=FALSE)
```

## Loading and preprocessing the data
1. First unzip the file and move it to current folder  
1. Make sure the current directory is set correctly  
1. Load the activity data  
```{r}
setwd("~/GitHub/RepData/RepData_PeerAssessment1")
rawdata <- read.csv("./activity.csv")
```


## What is mean total number of steps taken per day?
1. Make a histogram of the total number of steps taken each day
```{r}
totaldaily <- aggregate(list(total=rawdata$steps), list(date = rawdata$date), FUN=sum, na.rm=TRUE)
hist(totaldaily$total)
```
  
  You can also check total per day by plotting

```{r, fig.pos='H'}
barplot(totaldaily$total, names.arg=totaldaily$date)
```

2. Calculate and report the mean and median total number of steps taken per day
```{r}
totaldailyMean =mean(totaldaily$total, na.rm=TRUE)
totaldailyMedian = median(totaldaily$total, na.rm=TRUE)

```
  
  The mean of total number of steps taken per day is `r totaldailyMean`  
  The median of total number of steps taken per day is `r totaldailyMedian`
  
## What is the average daily activity pattern?

1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
 avgAcrossDays <- aggregate(list(avg=rawdata$steps), list(interval = rawdata$interval), FUN=mean, na.rm=TRUE)
 plot(avgAcrossDays$interval, avgAcrossDays$avg, type="l", xlab="Interval", ylab="Average Steps")
```
 
2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
maxInterval <- avgAcrossDays[which.max( avgAcrossDays[,2]),1]
```

  The interval:`r maxInterval` contains the maximum number of steps
  
## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?



